Confirmation of \srcfull{} as a long period radio transient

### 2024-12-08 paper/main.tex
Added (empty) sections in draft paper

\section{Introduction} \label{sec:intro}

@@

\begin{deluxetable*}{lcl}
\tablecaption{Known LPTs, arranged in ascending order of period\label{tbl:lpts}}
\tablehead{
\colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
 & \colhead{(min)} & 
} 
\startdata
%AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
%ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
%J1912-4410 & 5.3 &  \\
CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
ASKAP J175534.9-252749.1   & 69.8 & \citet{2024MNRAS.535..909D} \\
GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
ASKAP J1839-0756           & 387  & \todo{Lee} \\
\enddata
%\tablecomments{This is a sample table. Add more rows as needed, and include notes in this area.}
\end{deluxetable*}

>>>>

\section{Introduction} \label{sec:introduction}

@@

\begin{deluxetable*}{lcl}
\tablecaption{Known and candidate LPTs, arranged in ascending order of period\label{tbl:lpts}}
\tablehead{
\colhead{LPT} & \colhead{Period} & \colhead{References} \\ 
 & \colhead{(min)} & 
} 
\startdata
%AR Scorpii (J162147.28-225310.3) & 1.97 &  \\
%ASKAP J175154.89-255135.3 & ${\sim}$3.6 &  \\
%J1912-4410 & 5.3 &  \\
CHIME J0630+25             & 7.02 & \citet{2024arXiv240707480D} \\
GLEAM-X J162759.5-523504.3 & 18.2 & \citet{2022Natur.601..526H} \\
GPM J1839-10               & 22.0 & \citet{2023Natur.619..487H} \\
ASKAP J1832-0911           & 44.3 & \todo{Wang} \\
ASKAP J193505.1+214841.0   & 53.8 & \citet{2024NatAs...8.1159C} \\
ASKAP J175534.9-252749.1   & 69.8 & \citet{2024MNRAS.535..909D} \\
GCRT J1745-3009            & 77.0 & \citet{2005Natur.434...50H} \\
ILT J1101+5521             & 126  & \citet{2024arXiv240811536D} \\
GLEAM-X J0704-37           & 175  & \citet{2024arXiv240815757H} \\
ASKAP J1839-0756           & 387  & \todo{Lee} \\
\enddata
\end{deluxetable*}

\section{Observations} \label{sec:observations}

\subsection{MWA} \label{sec:mwa}

\subsection{ASKAP} \label{sec:askap}

\subsection{MeerKAT} \label{sec:meerkat}

\begin{deluxetable*}{cccccl}
\tablecaption{Pulse detections}
\tablehead{
\colhead{Obs start} & \colhead{Duration} & \colhead{Telescope} & \colhead{$\nu$} & \colhead{$\Delta\nu$} & Notes \\ 
\colhead{time (UTC)} & \colhead{(s)} & & \colhead{(MHz)} & \colhead{(MHz)} & 
} 
\startdata
2024-09-19 09:25:02 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & \\ % 1410773120 and 1410773416
2024-09-19 10:34:06 & 592\tablenotemark{a} & MWA & 184.96 & 30.72 & \\ % 1410777264 and 1410777560
2024-09-19 12:57:10 & 296 & MWA & 184.96 & 30.72 & \\ % 1410785848
2024-09-19 14:06:14 & 296 & MWA & 184.96 & 30.72 & \\ % 1410789992
2024-10-09 10:55:50 & 296 & MWA & 184.96 & 30.72 & \\ % 1412506568
2024-10-09 12:05:34 & 296 & MWA & 184.96 & 30.72 & \\ % 1412510752
2024-10-10 11:21:10 & 296 & MWA & 184.96 & 30.72 & \\ % 1412594488
2024-10-10 12:30:54 & 296 & MWA & 184.96 & 30.72 & (Pulse there but too much RFI) \\ % 1412598672
2024-10-11 10:36:46 & 296 & MWA & 184.96 & 30.72 & \\ % 1412678224
2024-10-11 11:46:30 & 296 & MWA & 184.96 & 30.72 & \\ % 1412682408
2024-10-12 11:02:06 & 296 & MWA & 184.96 & 30.72 & \\ % 1412766144
2024-10-12 12:11:50 & 296 & MWA & 184.96 & 30.72 & \\ % 1412770328
2024-10-13 10:17:42 & 296 & MWA & 184.96 & 30.72 & \\ % 1412849880
2024-10-13 11:27:26 & 296 & MWA & 184.96 & 30.72 & \\ % 1412854064
2024-10-14 10:43:02 & 296 & MWA & 184.96 & 30.72 & \\ % 1412937800
2024-10-14 11:52:46 & 296 & MWA & 184.96 & 30.72 & \\ % 1412941984
2024-10-16 10:23:58 & 296 & MWA & 184.96 & 30.72 & \\ % 1413109456
2024-10-16 11:33:42 & 296 & MWA & 184.96 & 30.72 & \\ % 1413113640
2024-10-17 11:59:02 & 296 & MWA & 184.96 & 30.72 & \\ % 1413201560
2024-10-19 10:30:14 & 296 & MWA & 184.96 & 30.72 & \\ % 1413369032
2024-10-19 11:39:58 & 296 & MWA & 184.96 & 30.72 & \\ % 1413373216
2024-10-19 13:54:36 & 601 & MeerKAT & 812.8 & 247.6 & (Two components) \\ % 1413381294
\enddata
\tablenotetext{a}{Two contiguous 296-second MWA observations were combined}
\end{deluxetable*}

\section{Analysis \& results} \label{sec:analysis}

\subsection{Timing solution and DM determination} \label{sec:timing_and_dm}

Following the positive identification of several pulses in the GPM data set, we did a grid search of periods that would result in an integer number of pulses between two widely spaced pulses.
A candidate period of $4186.4 \pm 0.1$ was found for which all detections fell within the same phase range ${\sim}0.05$.
% We further refined this by attempting to phase connect to Dougal's original pulse, and got $4186.33 \pm 0.02$ s, but this needn't be part of the story, since even the above was enough to motivate the MWA campaign that followed.
This motivated the follow-up MWA observations (under project code D0042) in which two consecutive pulses ${\sim}4190$ seconds apart were detected without any detectable emission between them, confirming our earlier estimate.
The lever arm afforded by both the GPM and D0042 detections proved sufficient to phase-connect to the original pulse published by \citet{2024MNRAS.535..909D}, yielding a refined period of $P = 4186.329 \pm 0.002$~s.

\subsection{Polarization} \label{sec:polarization}

\section{Discussion} \label{sec:discussion}

\section{Conclusions} \label{sec:conclusions}
